---
title: "QMM"
author: "Rohith"
date: "2022-09-23"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#installation("lpSolve")

library("lpSolve") #Activation of lpSolve Package
```

To solve the problem we need to define the objective, constraints, direction and constants

Objective Function

$$\text{Objective function is to } Max \hspace{.3cm} Z = 420 (A_1+A_2+B_3) + 360 (B_1+B_2+B_3) + 300 (C_1+C_2+C_3)$$

\$\$

\$\$

$$ \text {that can be written as } Z = 420A_1+360B_1+300C_1+420A_2+360B_2+300C_2+420A_3+360B_3+300C_3
$$

Subject to the following constraints

$$
A_1+B_1+C_1 \le 750 
$$

$$
A_2+B_2+C_2 \le 900 
$$

$$
A_3+B_3+C_3 \le 450
$$

$$
20A_1+15B_1+12C_1 \le 13000
$$

$$
20A_2+15B_2+12C_2 \le 12000
$$

$$
20A_3+15B_3+12C_3 \le 5000
$$

$$
A_1+A_2+A_3 \le 900
$$

$$
B_1+B_2+B_3 \le 1200
$$

$$
C_1+C_2+C_3 \le 750 
$$

Non Negativity Constraints

$$
 A_1,A_2,A_3,B_1,B_2,B_3,C_1,C_2,C_3 \ge 0
$$

The above constraints can be written as below

$$
A_1+B_1+C_1+0A_2+0B_2+0C_2+0A_3+0B_3+0C_3 \le 750  
$$

$$
 0A_1+0B_1+0C_1+A_2+B_2+C_2+0A_3+0B_3+0C_3 \le 900
$$

$$
 0A_1+0B_1+0C_1+0A_2+0B_2+0C_2+A_3+B_3+C_3 \le 450
$$

$$
20A_1+15B_1+12C_1+0A_2+0B_2+0C_2+0A_3+0B_3+0C_3 \le 13000
$$

$$
0A_1+0B_1+0C_1+20A_2+15B_2+12C_2+0A_3+0B_3+0C_3 \le 12000
$$

$$
0A_1+0B_1+0C_1+0A_2+0B_2+0C_2+20A_3+15B_3+12C_3 \le 5000
$$

$$
A_1+0B_1+0C_1+A_2+0B_2+0C_2+A_3+0B_3+0C_3 \le 900
$$

$$
0A_1+B_1+0C_1+0A_2+B_2+0C_2+0A_3+B_3+0C_3 \le 1200
$$

$$
0A_1+0B_1+C_1+0A_2+0B_2+C_2+0A_3+0B_3+C_3 \le 750
$$

Describing the Objective Function - f.obj

```{r}
f.obj <- c(420,360,300,420,360,300,420,360,300)
```

Describing the Constraints - f.con

```{r}

f.con <- matrix(c(1,1,1,0,0,0,0,0,0,
                  0,0,0,1,1,1,0,0,0,
                  0,0,0,0,0,0,1,1,1,
                  20,15,12,0,0,0,0,0,0,
                  0,0,0,20,15,12,0,0,0,
                  0,0,0,0,0,0,20,15,12,
                  1,0,0,1,0,0,1,0,0,
                  0,1,0,0,1,0,0,1,0,
                  0,0,1,0,0,1,0,0,1), nrow = 9, byrow=T)

```

Describing the Direction of the constraints - f.dir

```{r}
f.dir <- c('<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=',

           '<=')
```

Describing the constants i.e. the right hand side values - f.rhs

```{r}
f.rhs <- c(750,900,450,13000,12000,5000,900,1200,750)
```

Calling the lp function to solve the problem basing the objective function i.e. to maximize the profits

```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)
```

Calling the lp function again to get the values for the variables defined above

```{r}
lp('max',f.obj,f.con,f.dir,f.rhs)$solution
```

